### 2014-08-04 paper/paper.tex
Wrote about the results a bit

%TODO Feature Selection

@@

\subsection{Number of features}
\label{ssection:numfeatures}

@@

@@

The baseline for this project is established by running the Maximum Entropy
classifier without any stopword removal, uncommon word removal, Or feature
normalization. The F-score that is achieved is 50.72.

%TODO write something here about the method

@@

@@

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r|l|}
        \hline
        Team       & F \\
        \hline
        NRC-Canada & 69.02 \\
        GU-MLT-LT  & 65.27 \\
        teragram   & 64.86 \\
        BOUNCE     & 63.53 \\
        KLUE       & 63.06 \\
        AMI\&ERIC  & 62.55 \\
        FBM        & 61.17 \\
        AVAYA      & 60.84 \\
        SAIL       & 60.14 \\
        UT-DB      & 59.87 \\
        FBK-irst   & 59.76 \\
        nlp.cs.aueb.gr & 58.91 \\
        UNITOR     & 58.27 \\
        LVIC-LIMSI & 57.14 \\
        Unigon     & 56.96 \\
        NILC\_USP  & 56.31 \\
        DataMining & 55.52 \\
        ECNUCS     & 55.05 \\
        nlp.cs.aueb.gr & 54.73 \\
        ASVUniOfLeipzig & 54.56 \\
        SZTE-NLP   & 54.33 \\
        CodeX      & 53.89 \\
        Oasis      & 53.84 \\
        NTNU       & 53.23 \\
        \textbf{Best MaxEnt}& \textbf{52.81} \\
        UoM        & 51.81 \\
        \textbf{Best Navie Bayes}& \textbf{50.96} \\
        SSA-UO     & 50.17 \\
        SenselyticTeam & 50.10 \\
        $\ldots$   & $\ldots$ \\
        9 more teams &  \textless\ 50 \\
        \hline
        Majority Baseline & 29.19 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Comparison of constrained classifiers sumitted to the SemEval-2013
        workshop. Sorted by F-score.}
    \label{table:comparison}
\end{table}
%TODO fix this table

@@

>>>>

%TODO Feature Selection
%TODO mention bag of words

@@

The baseline for this project is established by running the Maximum Entropy
classifier without any stopword removal, uncommon word removal, Or feature
normalization. The F-score that is achieved is \textbf{50.72}.

%TODO consider cleaning the text up here

The following experiments examine the results of the Maximum Entropy classifier
and the Naive Bayes classifier with various feature selection methods turned on
or off. The `Baseline' experiment refers to no feature selection. The `Just
Stopwords' experiment refers the only removing stopwords. The `Just Uncommon'
experiment refers to only removing words with a document frequency of one. The
`Just Normalization' experiment refers to only applying feature normalization
mechanisms. The `All' experiment refers to testing the classifier with all of
the previous feature selection methods turned on.

%TODO add references to the feature selection section

\subsubsection{Number of features}
\label{ssection:numfeatures}

@@

%TODO check these results

@@

%TODO clarify

@@

As Table \ref{table:maxent-results} shows `All' experiment provides the best
results over the baseline. The `Just Stopwords' experiment actually provides
slightly worse results then the baseline indicating that in context of Tweets
with so few features in each example every feature counts. The `Just Uncommon'
experiment does not provide very significant gains when used alone. This is
potentially due to the fact that with out normalization turned, features such
as `just' are `Just' are determined to be different and may be removed if each
only occur once.

@@

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r|l|}
        \hline
        Team       & F \\
        \hline
        NRC-Canada & 69.02 \\
        GU-MLT-LT  & 65.27 \\
        teragram   & 64.86 \\
        BOUNCE     & 63.53 \\
        KLUE       & 63.06 \\
        AMI\&ERIC  & 62.55 \\
        FBM        & 61.17 \\
        AVAYA      & 60.84 \\
        SAIL       & 60.14 \\
        UT-DB      & 59.87 \\
        FBK-irst   & 59.76 \\
        nlp.cs.aueb.gr & 58.91 \\
        UNITOR     & 58.27 \\
        LVIC-LIMSI & 57.14 \\
        Unigon     & 56.96 \\
        NILC\_USP  & 56.31 \\
        DataMining & 55.52 \\
        ECNUCS     & 55.05 \\
        nlp.cs.aueb.gr & 54.73 \\
        ASVUniOfLeipzig & 54.56 \\
        SZTE-NLP   & 54.33 \\
        CodeX      & 53.89 \\
        Oasis      & 53.84 \\
        NTNU       & 53.23 \\
        UoM        & 51.81 \\
        \textbf{MaxEnt}& \textbf{50.96} \\
        SSA-UO     & 50.17 \\
        SenselyticTeam & 50.10 \\
        $\ldots$   & $\ldots$ \\
        9 more teams &  \textless\ 50 \\
        \hline
        Majority Baseline & 29.19 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Comparison of constrained classifiers sumitted to the SemEval-2013
        workshop. Sorted by F-score.}
    \label{table:comparison}
\end{table}
%TODO add naive bayes

@@

\subsection{Stopword list}
\label{ssection:stopwords}

The list of stopwords was acquired at \href{holla}{www.ranks.nl/stopwords} and
is as follows:

a, about, an, are, as, at, be, by, com, for, from, how, in, is, it, of, on, or,
that, the, this, to, was, what, when, where, who, will, with
